---
title: "Homework 2"
author: "Miles Robinson"
date: "2024-03-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(moderndive)
```

## Load the dataset

Load the "early_january_weather" dataset

```{r}
data(early_january_weather)
```

## Description of the data

The data set contains a total of 15 variables/columns, and 358 subjects/rows. The primary/first row of the data set is the location, which appears to contain airport codes. Other variables include dates, temperatures, and other weather factors. 


```{r}
skimr::skim(early_january_weather)
```

## Size of the data

The data set contains a total of 15 variables/columns, and 358 subjects/rows. 

```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```

## Average temperature

The average temperature of the data set: 

```{r}
mean(early_january_weather$temp)
```

## Plot of data

Scatterplot of temp (y) vs time_hour (x): 

```{r}
data(early_january_weather)
ggplot(data = early_january_weather)+                   
  geom_point(                             
    mapping = aes(x = time_hour, y = temp),    
    color = "red")

# The data shows a general increase in the temperature throughout the month. Incremental increases followed by decreases can be observed on a daily basis. 
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
